---
title: "Assignment2"
author: "Chuong Bao Thy Lai"
date: "9/1/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, warning= FALSE, results='hide'}
set.seed(123)
library(readxl)
library(ggplot2)
library(rsample)
library(rpart)
library(rpart.plot)
library(caret)
library(randomForest)
library(rattle)
```

```{r}
wine <- read.csv('winequality-red.csv')
head(wine)
```

```{r, results='hide'}
#histogram of the frequency of wine quality ratings
table(wine$quality)
wine$quality <- as.factor(wine$quality)
str(wine$quality)
quality <- as.numeric(wine$quality)
```
```{r}
hist(quality)
```
```{r}
# split data into training and testing set using an 80% training, 20% testing split
set.seed(123)
wine_split  <- initial_split(wine, prop = 0.8, 
                              strata = "quality")
wine_train  <- training(wine_split)
wine_test   <- testing(wine_split)
```

```{r}
#build a decision tree model
wine_1 <- rpart(
  formula = quality ~ .,
  data    = wine_train,
  method  = "class"
)
```

```{r}
prp(wine_1)
```

```{r}
fancyRpartPlot(wine_1) 
```


```{r}
pred <- predict(wine_1,wine_test,type="class")
confusionMatrix(table(pred,wine_test$quality))
```

## 4 Random Forest

```{r}
barplot(table(wine$quality))
```
```{r}
wine2 <- read.csv('winequality-red.csv')
wine2$taste <- ifelse(wine2$quality < 5, "bad", "good")
wine2$taste[wine2$quality == 5] <- "normal"
wine2$taste[wine2$quality == 6] <- "normal"
wine2$taste <- as.factor(wine2$taste)
str(wine2$taste)
```
```{r}
ggplot(wine2, aes(taste))+
  geom_histogram(stat="count", color = "black", fill="blue")
```
```{r}
set.seed(123)
wine_split2 <- initial_split(wine2, prop = 0.8, 
                              strata = "taste")
wine_train2  <- training(wine_split2)
wine_test2   <- testing(wine_split2)
```

```{r}
wine_rf1 <- randomForest(taste~.-quality, data=wine_train2)
wine_rf1
```

```{r}
pred1 <- predict(wine_rf1, newdata=wine_test2)
confusionMatrix(pred1, wine_test2$taste)
```

```{r}
predtable <- table(pred1, wine_test2$taste)
predtable
```
```{r}
sum(diag(predtable))/nrow(wine_test2)
```
We build a decision tree to predict the quality of a wine. Our tree allows us to ask a yes-no question about each feature. For example, if a wine has alcohol >12 and sulfate <0.69, the quality of the wine is 6. Our model has an accuracy is 0.5701. In order to increase the accuracy, we use the Random Forest technique that builds a large collection of de-correlated trees to improve predictive performance. The next model has an accuracy is 0.8656. 
